The planner reports the assignment and the id of the case back to the agent. The assignment information is used to transfer the expected effects to the current situation since this information is stored with the ids of the original objects, which are likely different in another situation.
Because the order is known, the old IDs can be mapped to the IDs of the objects in the current situation with the assignment information. As demonstrated in section \ref{lst:case-prolog}, the assignment in Prolog happens as a List.
The original list of affected IDs can then be used with the newly obtained list of object IDs in the current scene to replace the original IDs in the effects with the new IDs, thus translating them and obtaining expected effects on the new objects, as can be seen in listing \ref{lst:map}

\begin{lstlisting}[label=lst:map, caption=case information outside of Prolog]
// original case with old IDs
{
  "effects": {
    "movedIDs": ["wood0", "wood7", "ice8", "ice1"],
    "destroyedIDs": ["ice10", "pig0"]
  },
}
// original order => [wood0, wood7, ice8, ice1, ice10, pig0]
// assignment:
["wood5", "wood18", "ice1", "ice2", "ice5", "pig2"]
// expected effects:
{
  "effects": {
    "movedIDs": ["wood5", "wood18", "ice1", "ice2"],
    "destroyedIDs": ["ice5", "pig2"]
  },
}
\end{lstlisting}


Now the expected effects of the shot are known, i.e. which objects are expected to move or be destroyed.
Once the shot has been executed, the effect detection strategy described in \ref{subsec:impl-effects} is used to obtain the actual effects.
At this point, the case can be refined using the information: If the effects match even though some relations were violated, those relations probably were not important to the applicability of the case and can thus be relaxed or even discarded.
If the effects do not match and relations were violated, those probably are important to the applicability and a new case should be generated.

If the effects do not match even though all relations matched, the relations were presumably relaxed too much and either the relations need to be tightened or the case needs to be penalized or removed. Penalization of cases could be achieved by associating cases with a confidence score which is increased/decreased after successful/unsuccessful execution and favoring cases with higher confidence scores.


Further research could be conducted here. For example, whether observed and expected effects match depends on how they are used. In this implementation, it is sufficient if the case destroys the targets it promised to, regardless of what happened to other objects.
If used in a more complex planning environment, where cases might also be used to clear a way for future shots, this might be insufficient. Whether an object that should have been destroyed but was moved or vice versa constitutes a match or a violation is also dependent on what purpose effects are used for.