\section{Background}\label{sec:background}

\subsection{Case-Based Reasoning}
Case-Bases Reasoning (CBR) is a method that dates back to the 1980s. It works similarly to how humans operate: Confronted with a novel situation, humans tend to think of similar situations they encountered in the past and try to adapt their previous solution to handle the new scene. Cases do not always have to be positive, i.e. provide a path to success, they can also be used to avoid errors.\cite{Kolodner1992} For this paper, only positive instances of cases will be considered.

One key advantage of CBR over approaches like Deep Learning is that it requires less data and less time to be spent on training. Since the agent generates cases from its own experiences, general knowledge of the the problem domain is not required.\cite{CBR-issues-variations-approaches}

The core \ac{CBR} cycle consists of four steps: Case Retrieval, Adaptation, and Evaluation.\cite{Kolodner1992}
Confronted with a situation that needs to be solved, a database of known cases is queried and the case that best matches the problem is retrieved. A case consists of at least a description of the situation in which it is applicable and a solution for the problem. Usually situations are similar but not identical, thus the solution may need to be adapted to fit the new situation. The adapted solution can then be executed and its effects can be used to evaluate and potentially update the case.


Recently, CBR has been used in medical fields\cite{medical1, medical2} and robotics\cite{QCBR}, but also for language models \cite{text, text2}. % TODO: citation needed

\subsection{Qualitative Representations and Reasoning}
Unlike quantitative representations, qualitative representations try to abstract from actual values, thus increasing generalizability.


% What is CBR?
% Current Research Status of CBR?
% Why quantitative? -> abstraction from values
\subsection{Previous Work}
In previous work, we devised a strategy to use case-based reasoning to allow the agent to remember good shots und use them again in similar scenarios, even though the strategy that originally produced this shot may not have a high priority.
Case-based reasoning is a strategy in artificial intelligence that aims to modify known solutions to problems in order to make them applicable to the problem at hand.
To do so, relevant information about the problem and the associated solution need to be stored and similarity between problems must be judged.
If two problems are similar enough, the solution can be transformed to solve the new problem.
In out implementation, similarity between scenarios was judged quantitatively based on position and size of objects.

\cite{QCBR} discusses a similar problem, applying a combination of \ac{CBR} and Reinforcement Learning to robotic soccer players.
The qualitative spatial representation framework they use, \ac{EOPRA} is one of the options discussed in \ref{subsec:impl-relations}.



\subsection{Goals \& Approaches}

Now the goal is to devise a qualitative solution.
Instead of absolute positions, relations between objects shall be considered when determining applicability of cases.
This could lead to an improvement in performance compared to the quantitative approach, as that came with limitations as to what objects were considered and when two scenes where estimated to be transferable. % TODO: should evaluation also be run against the quantitative approach?
For example, a few pixels could make the difference between an object being irrelevant or an actual obstacle.
But due to thresholds we used in the quantitative approach, this distinction may not occur. % TODO: add image of a level where this could be an issue
% TODO: Check wether this level could then be beaten using QualCBR

The main objective will consist of comparing subsets of quantitative relations to find those that maximize the score the agent can achieve in-game as well as finding a suitable method for quantifiying scene similarity.

